---
title: "Avast"
author: "Ana Preciado"
date: "May 21, 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE) 
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. We are analyzing the effectiveness of this drug for all participants. We are considering the entire observed population. We got the data from avast, which consists of 6 variables: x, treatment, sex, infected, ivdrug, and LBGT.  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
The methods that are used for this experiment are Pearson's Chi-squared test, Fisher's Exact Test for Count Data, and barcharts for graphical descriptive results.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !--> 

```{r}
barchartGC(~infected+treatment, data=avast, type = "percent")
``` 

According to the barchart, the participants who received the drug in this study had a lower percentage of likelihood of them being infected with aids. About 40% of the participants taking the drug became infected with aids, whereas about 50% of the participants taking the placebo became infected with aids. This proves that the drug is effective for the participants. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!--> 

```{r}
mytable5 <- xtabs(~infected+treatment, data=avast)
rowPerc(mytable5) 
colPerc(mytable5)
```
According to the row and column percent test, participantas who took the drug were 40.87% likely to become infected with aids and the participants who did not take the drug were 49.10% likely to become infected. Participants had less of chance of becoming infected if they received the drug. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!--> 

We assume the null hypothesis to be: 

$H_0$ : There is a relationship between being a participant and the positive effectiveness of the drug.

$H_A$ : There is no relationship between being a participant and the positive effectiveness of the drug.

```{r}
chisqtestGC(~infected+treatment, data=avast)
```
```{r}
fisher.test(mytable5)
```
We accept the null hypothesis in this case because there is a relationship between being a participant and the drug being effective. According to the Chi-Squared Test the counts expected by the null were that participants taking the drug would be less likely to become infected with aids than those that were taking the placebo. This was proven correct because when the study was done only 423 participants who took the drug became infected and only 612 participants who took the placebo became infected. 

According to the Fisher's Exact Test the odds ratio of a participants taking the drug and getting aids is 0.71. Therefore they have about 0.71 of a chance of getting aids if they take drug over those taking the placebo

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!--> 

In this study we observed the statistical odds of getting aids for the participants who took the new drug. The relationship between being a participant and taking the drug had a positive effect on the observed volunteers. Those who took the drug were more less to become infected with aids than those who took the placebo. This study proves that this drug is effective for people to take in order to become immune from aids.
