---
title: "Aides Drug_gender"
author: "Ana Preciado"
date: "May 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE) 
female <- filter(avast, sex == "F")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. We are analyzing the effectiveness of this drug for females. We are considering the female population. We got the data from avast, which consists of 6 variables: x, treatment, sex, infected, ivdrug, and LBGT. 

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!--> 

The methods that are used for this experiment are Pearson's Chi-squared test, Fisher's Exact Test for Count Data, and barcharts for graphical descriptive results.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !--> 

```{r}
barchartGC(~infected+treatment, data=female, type = "percent")
```

According to the barchart, the females who received the drug in this study had a higher percentage likelihood of them being infected with aids. About 60% of females taking the drug bacame infected with aids, whereas only about 40% of females not taking the drug became infected with aids.  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!--> 

```{r}
mytable2 <- xtabs(~infected+treatment, data=female)
rowPerc(mytable2) 
colPerc(mytable2)
```

According to the row and column percent test, the women who took the drug were 58.82% likely to become infected with aids and the women who did not take the drug  were only 48.06% likely to become infected. 


## Inferential Results 

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->   

We assume the null hypothesis to be: 

$H_0$ : There is a relationship between being female and the positive effectiveness of the drug.

$H_A$ : There is no relationship between being female and the positive effectiveness of the drug.
```{r}
chisqtestGC(~infected+treatment, data=female)
```
```{r}
fisher.test(mytable2)
```

We reject the null hypothesis in this case because there is no relationship between being female and the drug being effective. According to the Chi-Squared Test the counts expected by the null were that the females taking the drug would be less likely to become infected with aids than those that were taking the placebo, but when the study was conducted it showed the opposite which was that those taking the drug were more likely to get aids than those taking the placebo. 

According to the Fisher's Exact Test the odds ratio of a female taking the drug and getting aids is 1.5. Therefore they have a 1.5 chance of getting aids over those taking the placebo.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!--> 

In this study we observed the statistical odds of getting aids for females who took the new drug. The relationship between being female and taking the drug had a negative effect on the observed volunteers. Those who took the drug were more likely to become infected with aids than those who took the placebo. This study proves that this drug is not effective for females to take in order to become immune from aids.
